\plaintitle

### 2016-05-18 paper/paper.tex
links voor related work opgezocht

@@

%http://courses.ischool.berkeley.edu/i247/f05/readings/Baldonado_MultipleViews_AVI00.pdf
%http://lemonchiu.github.io/NBA-Visualization/
%http://peterbeshai.com/buckets/app
%https://source.opennews.org/en-US/articles/nyts-512-paths-white-house/
%http://projects.fivethirtyeight.com/complete-history-of-the-nba/#warriors
%http://www.theguardian.com/news/datablog/interactive/2013/jun/03/premier-league-season-visualised
%http://gizmodo.com/5927503/all-the-major-sport-competitions-since-1903-condensed-in-beautiful-circular-graphics
%http://www.nbaplayoffsbracket.com/2016/index.php
%http://inf.ufrgs.br/~lsguedes/skooth/Publications_&_Works_files/nbavis_final.pdf
%https://en.wikipedia.org/wiki/National_Basketball_Association

>>>>

Many visualizations of NBA data are focused on the "shot-chart".  This of individual players, multiple players together or all the teams
This is almost a standard in visualizations about NBA data where even the code for making short charts is easily found ~\cite{shotchartpython}~\cite{shotchartr}~\cite{shotchartapp}.

This paper (http://inf.ufrgs.br/~lsguedes/skooth/Publications_&_Works_files/nbavis_final.pdf) describes

@@

%General
%https://en.wikipedia.org/wiki/National_Basketball_Association
%http://courses.ischool.berkeley.edu/i247/f05/readings/Baldonado_MultipleViews_AVI00.pdf
%http://www.interactiondesign.us/courses/2011_AD690/PDFs/Shneiderman_1996.pdf
%http://workshop.sportvis.com/
%http://www2.parc.com/istl/groups/uir/publications/items/UIR-1986-02-Mackinlay-TOG-Automating.pdf
%http://www.cc.gatech.edu/~john.stasko/papers/infovis06.pdf

%Shot charts
%http://peterbeshai.com/buckets/app
%http://vorped.com/1-nba/2015-2016/player/6667/emmanuel-mudiay/
%https://github.com/amatlin/NBAvis
%https://thedatagame.com.au/2015/09/27/how-to-create-nba-shot-charts-in-r/
%http://savvastjortjoglou.com/nba-shot-sharts.html?utm_source=Python+Weekly+Newsletter&utm_campaign=5185ff0538-Python_Weekly_Issue_202_July_30_2015&utm_medium=email&utm_term=0_9e26887fc5-5185ff0538-312727397
%http://www.sloansportsconference.com/wp-content/uploads/2012/02/Goldsberry_Sloan_Submission.pdf
%http://vis.berkeley.edu/courses/cs294-10-sp10/wiki/images/archive/a/a2/20100511091342!Stephen_Chu_-_Information_Visualization_in_the_NBA_-_The_Shot_Chart_16.pdf
%http://toddwschneider.com/posts/ballr-interactive-nba-shot-charts-with-r-and-shiny/

%Standings
%https://source.opennews.org/en-US/articles/nyts-512-paths-white-house/
%http://projects.fivethirtyeight.com/complete-history-of-the-nba/#warriors
%http://www.theguardian.com/news/datablog/interactive/2013/jun/03/premier-league-season-visualised
%http://gizmodo.com/5927503/all-the-major-sport-competitions-since-1903-condensed-in-beautiful-circular-graphics
%http://www.nbaplayoffsbracket.com/2016/index.php
%http://nyloncalculus.com/2015/08/07/as-nba-empires-rise-and-fall/
%http://inf.ufrgs.br/~lsguedes/skooth/Publications_&_Works_files/nbavis_final.pdf
%http://research.microsoft.com/pubs/64282/tvcg2007-adaptivitree.pdf
%http://www.student.kuleuven.be/~s0217391/mume/deliverables/paper.pdf

%Other
%https://graphics.stanford.edu/wikis/cs448b-10-fall/FP-RuthEric-HeddlestonKate?action=AttachFile&do=get&target=448bPaper.pdf
%http://www.scribblelive.com/blog/2014/03/20/the-power-of-sports-data-visualizing-passes-between-nba-players-offers-new-game-insights/
%http://lemonchiu.github.io/NBA-Visualization/
